Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
notes.
Users graph.

\documentclass{article}  
\usepackage{url}

@@

@@

@@

@@

>>>>

\documentclass{article}  
\usepackage{graphicx}
\usepackage{url}

@@

The confidentiality provided by HTTPS

Alternate domain fronting: use just an IP (no DNS and no SNI).

@@

\section{Threat model}

Censor allows www.google.com (or an IP); forbids appspot.com.

\section{Architecture}

@@

Two big things: list of ciphersuites and extensions.

@@

\section{Deployment}

\begin{figure}
\includegraphics[width=\linewidth]{clients-meek}
\caption{Number of concurrent users using the meek transport,
as reported by the Tor Metrics Portal.
Missing parts of the graph are caused by missing data at the metrics portal.
}
\label{fig:clients}
\end{figure}

Figure~\ref{fig:clients} shows the number of concurrent users of meek between January and May~2014,
as reported by the Tor Metrics Portal~\cite{metrics-meek}.
The number of concurrent users is estimated by counting directory requests made over the transport~\cite{counting-daily-bridge-users}.
